Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
new paper + corrected typos

Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
involves a trade or a Q&A with the thread poster. We sum each algorithm's score and determine based on that score whether the comment is 
positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
percentage of comments involving a trade and percentage of comments with a Q&A.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{PaymentChart.png}
	\caption{Sentiment Analysis Chart}
\end{figure}

>>>>

Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
involves a trade or a Q\&A with the thread poster. We sum each algorithm's score 
and determine based on that score whether the comment is 
positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
percentage of comments involving a trade and percentage of comments with a Q\&A.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{PaymentChart.png}
	\caption{Payment Method Chart}
\end{figure}
